Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
reference table 1 again

<!--JM: not entirely sure what scattered appearance refers to-->
Buffering is most often applied in coordinate space due to the scattered appearance of observations in this space.
However, this method could be easily extended to a 2D + time setting.
<!-- JM: I guess you mean that you could have placed buffering also into spatiotemporal partition. I would advise to say so instead of letting the reader guess.-->
Since \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods.

>>>>

<!--JM: not entirely sure what scattered appearance refers to-->
Buffering is most often applied in coordinate space due to the scattered appearance of observations in this space.
However, this method could be easily extended to a 2D + time setting.
<!-- JM: I guess you mean that you could have placed buffering also into spatiotemporal partition. I would advise to say so instead of letting the reader guess.-->
Since \pkg{mlr3spatiotempcv} supports two spatial-only "buffering" implementations, (1) "Spatial buffering" from package \pkg{blockCV} and (2) "Leave-one-disc-out cross-validation" from \pkg{sperrorest}, buffering was attributed to the category of spatial partitioning methods (see Table \@ref(tab:sptcv-methods)).
